---
title: "ICI immunosuppression review"
author: "Rik J. Verheijden"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
---

# Prepare workspace

Empty workspace
```{r echo = T, eval = T}
rm(list = ls())
```

Set working directory
```{r echo = F, eval = T}
setwd("/folder/filepath")
```

Install required packages
```{r echo = T, eval = F, warning = F, error=F, message=F}
install.packages("readxl")
install.packages("dplyr")
install.packages("ggplot2")
install.packages("ggpubr")
```

Activate packages
```{r echo = T, eval = T, warning = F, error=T, message=F}
library(readxl)
library(dplyr)
library(ggplot2)
library(ggpubr)
```

#Load Excel file

Define file path: change to file label of input file; note that file label should end with .xlsx
```{r echo = T, eval = T, warning = T, error=T, message=T}
path <- "Review_IS_ICI_forestplot_data_2023-02-10_RJV.xlsx"
```

Load all Excel sheets as separate labeld data frames automatically
```{r echo = T, eval = T, warning = T, error=T, message=T}
for (i in excel_sheets(path)) {
  assign(i, read_xlsx(path, sheet = i))
}
rm(i,path)

```

Some formatting:

-   Change commas to dots
-   Right-align y-axis labels
-   Sort y-axis labels by cut-off dose (if mg/kg: reference person of 70kg assumed)
-   Add and right-align references

```{r echo = T, eval = T, warning = T, error=T, message=T}
#glucocorticoids
glucocorticoids$IS_dose <- gsub(",",".",glucocorticoids$IS_dose)
glucocorticoids$IS_dose_70 <- as.numeric(glucocorticoids$IS_dose_70)
glucocorticoids$label <- gsub(",",".",glucocorticoids$label)
glucocorticoids$label <- format(glucocorticoids$label, width = max(nchar(as.character(glucocorticoids$label))), justify = "right")
glucocorticoids$label <- factor(factor(glucocorticoids$label), levels = as.vector(glucocorticoids[order(glucocorticoids$IS_dose_70, decreasing = T),]$label))
glucocorticoids$ref <-  format(glucocorticoids$ref, width = max(nchar(as.character(glucocorticoids$ref))), justify = "right")
# glucocorticoids$ref <- ""

#2L_IS
`2L_IS`$IS_dose <- gsub(",", ".", `2L_IS`$IS_dose)
`2L_IS`$label <- gsub(",", ".", `2L_IS`$label)
`2L_IS`$label <- paste0(format(`2L_IS`$label, width = max(nchar(as.character(`2L_IS`$label))), justify = "right"))
`2L_IS`$label <- factor(factor(`2L_IS`$label), levels = as.vector(`2L_IS`[order(`2L_IS`$IS_dose, decreasing = T),]$label))
`2L_IS`$ref <- paste0(format(`2L_IS`$ref, width = max(nchar(as.character(`2L_IS`$ref))), justify = "right"))
# `2L_IS`$ref <- ""
```

# glucorticoids

We will now make Figure 2 of the review.

Specify which data to use
```{r echo = T, eval = T, warning = T, error=T, message=T}
data <- glucocorticoids
```

Add reference number to row label in superscript
```{r echo = T, eval = T, warning = T, error=T, message=T}
data <- data.frame(data)
labels <- lapply(1:nrow(data), FUN = function(x) bquote(.(as.character(data[x,"label"])) ^ .(as.character(data[x,"ref"]))))
names(labels) <- data$label
```

Specify desired columns to use for dots
```{r echo = T, eval = T, warning = T, error=T, message=T}
dot <- c("control_group", "ICI_homogeneous", "tumour_homogeneous", "indication_IS_irAE", 'immortal_time_bias')
```

Changes values to `+`, `-`, `X` or `?` depending on input.

```{r echo = T, eval = T, warning = T, error=T, message=T}
for (i in dot){
  data$i<- data.frame(data)[,i]
  data[,i]<- factor(dplyr::recode(data$i,
                                  "low"="+", "Low"="+",
                                  "some concerns"="-", "Some concerns"="-", "Some Concerns"="-", "intermediate"="-", "Intermediate"="-", "adjusted"="-", "Adjusted"="-",
                                  "high"="X", "High"="X",
                                  "unclear"="?", "Unclear"="?", "no information"="?", "No information"="?", "No Information"="?")
                    , levels = c("+", "-", "X", "?"))
  data$i <- NULL
}
```

## glucocorticoids - OS

Store data and select only patients for OS part of the plot
```{r echo = T, eval = T, warning = T, error=T, message=T}
data_backup <- data
data<- data[!is.na(data$n_OS),]
```

Determine maximum number of patients per study to scale point in forrest plot
```{r echo = T, eval = T, warning = T, error=T, message=T}
n_max_subset = max(data$n_OS, na.rm = T)
n_max_subset
```

Prespecify some values for the plot
```{r echo = T, eval = T, warning = T, error=T, message=T}
pointsize = 10
textsize = 12
n_max_total = 500
colorlegendtitle = "daily dose cut-off (mg)"
sizelegendtitle = "sample size"
```

Make base layer of forrest plot
```{r echo = T, eval = T, warning = T, error=T, message=T}
forrest_base <- ggplot(data, aes(y = label))+
  geom_vline(aes(xintercept=1), linetype = "longdash", color = "darkgrey")+
  scale_size_area(sizelegendtitle, max_size = 6*n_max_subset/n_max_total)+
  scale_x_continuous(trans = "log10")+
  coord_cartesian(xlim = c(.1,10), expand = T)+
  scale_fill_viridis_c(colorlegendtitle, direction = 1)+
  # scale_fill_viridis_d()+
  theme(legend.position = "none"
        # ,legend.key = element_rect(fill = "white")
        ,plot.title = element_text(hjust =0.5, size=textsize, face = "bold")
        ,panel.background = element_blank()
        # ,panel.grid.major = element_line(color = "lightgrey")
        ,axis.line.x = element_line(color = "black")
        ,axis.ticks.y = element_blank()
        ,axis.text.y = element_text(size = textsize, face = "bold", color = "black")
        ,axis.title.y = element_blank()
        ,axis.text.x = element_text(size = textsize, color = "black")
        ,axis.title.x = element_text(size = textsize)
        # ,plot.margin=unit(c(5,0,0,0), units = "lines")
        )
```

Make basis layer for table part of the plot
```{r echo = T, eval = T, warning = T, error=T, message=T}
tab_base <- ggplot(data, aes(x=1, y=label)) +
  labs(y=NULL, x= " ") + 
  theme(legend.position="none"
        ,plot.title = element_text(hjust=0.5, size=textsize, face = "bold") ## centering title on text
        ,axis.text.x=element_text(color="white", size = textsize) ## need text to be printed so it stays aligned with figure but white so it's invisible
        ,axis.title.x=element_text(color="white", size = textsize)
        ,axis.line=element_blank()
        ,axis.text.y=element_blank()
        ,axis.title.y=element_blank()
        ,panel.background=element_blank()
        ,axis.ticks=element_blank()
        # ,plot.margin=unit(c(30,0,0,0), units = "points")
        )
```

Make basis layer for dot part of the plot. We use the colors used in the [risk of bias tools that are propagated by the Cochrane Collaboration](riskofbias.info) from the [robvis package](https://github.com/mcguinlu/robvis).
```{r echo = T, eval = T, warning = T, error=T, message=T}
dot_base <- ggplot(data, aes(x=1, y=label)) +
  labs(y=NULL, x= " ") + 
  scale_colour_manual(values = c("+"="#02C100", "-"="#E2DF07", "X"="#BF0000", "?"="#4EA1F7"))+
  theme(legend.position="none"
        ,plot.title = element_text(hjust=0.5, size=textsize, face = "bold") ## centering title on text
        ,axis.text.x=element_text(color="white", size = textsize) ## need text to be printed so it stays aligned with figure but white so it's invisible
        ,axis.title.x=element_text(color="white", size = textsize)
        ,axis.line=element_blank()
        ,axis.text.y=element_blank()
        ,axis.title.y=element_blank()
        ,panel.background=element_blank()
        ,axis.ticks=element_blank()
        # ,plot.margin=unit(c(30,0,0,0), units = "points")
        )
```

Make the forrest plot
```{r echo = T, eval = T, warning = T, error=T, message=T}
p <- forrest_base +
  geom_linerange(aes(xmin = HR_OS_CI_lower, xmax = HR_OS_CI_upper)
  ) + geom_point(aes(x = HR_OS
                     , size = n_OS
                     # , fill = IS_dose_70
                     )
                 , shape = 22
                 , fill = "black"
  ) + scale_y_discrete(labels = labels
  ) + labs(x = "hazard ratio (95% CI)"
       ,title = "Overall Survival"
  )
```

Add arrowhead if confidence band exceeds axis limits
```{r echo = T, eval = T, warning = T, error=T, message=T}
if(nrow(data[data$HR_OS_CI_upper>10,])>0){
  p<- p + 
    geom_segment(data = data[data$HR_OS_CI_upper>10,]
                 ,aes(x = HR_OS_CI_lower, xend = Inf, yend = label)
                 ,arrow=arrow(length = unit(.3, "cm"), type = "closed")
    )
}
```

Make table part of plot
```{r echo = T, eval = T, warning = T, error=T, message=T}
n <- tab_base + 
  geom_text(aes(label = n_OS)
  ) + labs(title = "n"
  )

HR <- tab_base +
  geom_text(aes(label = paste0(format(round(HR_OS,2),nsmall=2,scientific=FALSE)," (",format(round(HR_OS_CI_lower,2),nsmall=2,scientific=FALSE),"; ", format(round(HR_OS_CI_upper,2),nsmall=2,scientific=FALSE),")"))
  ) + labs(title = "HR (95% CI)"
  )

dose <- tab_base +
  geom_text(aes(label = IS_dose)
  ) + labs(title = "dose cut-off"
  )
```

Make dot-part of plot
```{r echo = T, eval = T, warning = T, error=T, message=T}
ICI <-dot_base +
  geom_point(aes(color = ICI_homogeneous), size = pointsize, shape = 16
  ) + geom_text(aes(label = ICI_homogeneous), fontface = "bold"
  ) + labs(title = "ICI"
  )

tumour <- dot_base +
  geom_point(aes(color = tumour_homogeneous), size = pointsize, shape = 16
  ) + geom_text(aes(label = tumour_homogeneous), fontface = "bold"
  ) + labs(title = "tumour"
  )

indication <- dot_base +
  geom_point(aes(color = indication_IS_irAE), size = pointsize, shape = 16
  ) + geom_text(aes(label =indication_IS_irAE), fontface = "bold"
  ) + labs(title = "IS only for irAE"
  )

immortal_time_bias <- dot_base +
  geom_point(aes(color = immortal_time_bias), size = pointsize, shape = 16
  ) + geom_text(aes(label =immortal_time_bias), fontface = "bold"
  ) + labs(title = "immortal time"
  )
```

Combine all above together into one plot
```{r echo = T, eval = T, warning = T, error=T, message=T}
forrest_GC_OS <- ggarrange(p,HR,n,dose,ICI,tumour,indication,immortal_time_bias, nrow = 1, widths = c(8,2,1,2,1,1,1,1)
          # ,labels = c("\nOverall Survival", "\nHR (95% CI)", "\nn", "dose\ncut-off", "\nICI", "tumour\n", "\nirAE", "indication\n", "\nimmortal time")
          # ,label.x = 0.5, hjust = 0.5, label.y = 1.1
          ,font.label = list(size =textsize, face = "bold")
          ,common.legend = T, legend = "none"
          ) + theme(plot.margin = unit(c(0.5,0.4,0,0), units = "strwidth", data = "immortal time")
          )
forrest_GC_OS
```

## glucocorticoids - PFS

Repeat all above for the PFS plot.
```{r echo = T, eval = T, warning = T, error=T, message=T}
data <- data_backup
data<- data[!is.na(data$n_PFS),]
n_max_subset = max(data$n_PFS, na.rm = T)


forrest_base <- ggplot(data, aes(y = label))+
  geom_vline(aes(xintercept=1), linetype = "longdash", color = "darkgrey")+
  scale_size_area(sizelegendtitle, max_size = 6*n_max_subset/n_max_total)+
  scale_x_continuous(trans = "log10")+
  coord_cartesian(xlim = c(.1,10), expand = T)+
  scale_fill_viridis_c(colorlegendtitle, direction = 1)+
  # scale_fill_viridis_d()+
  theme(legend.position = "none"
        # ,legend.key = element_rect(fill = "white")
        ,plot.title = element_text(hjust =0.5, size=textsize, face = "bold")
        ,panel.background = element_blank()
        # ,panel.grid.major = element_line(color = "lightgrey")
        ,axis.line.x = element_line(color = "black")
        ,axis.ticks.y = element_blank()
        ,axis.text.y = element_text(size = textsize, face = "bold", color = "black")
        ,axis.title.y = element_blank()
        ,axis.text.x = element_text(size = textsize, color = "black")
        ,axis.title.x = element_text(size = textsize)
        # ,plot.margin=unit(c(5,0,0,0), units = "lines")
  )

tab_base <- ggplot(data, aes(x=1, y=label)) +
  labs(y=NULL, x= " ") + 
  theme(legend.position="none"
        ,plot.title = element_text(hjust=0.5, size=textsize, face = "bold") ## centering title on text
        ,axis.text.x=element_text(color="white", size = textsize) ## need text to be printed so it stays aligned with figure but white so it's invisible
        ,axis.title.x=element_text(color="white", size = textsize)
        ,axis.line=element_blank()
        ,axis.text.y=element_blank()
        ,axis.title.y=element_blank()
        ,panel.background=element_blank()
        ,axis.ticks=element_blank()
        # ,plot.margin=unit(c(30,0,0,0), units = "points")
  )

dot_base <- ggplot(data, aes(x=1, y=label)) +
  labs(y=NULL, x= " ") + 
  scale_colour_manual(values = c("+"="#02C100", "-"="#E2DF07", "X"="#BF0000", "?"="#4EA1F7"))+
  theme(legend.position="none"
        ,plot.title = element_text(hjust=0.5, size=textsize, face = "bold") ## centering title on text
        ,axis.text.x=element_text(color="white", size = textsize) ## need text to be printed so it stays aligned with figure but white so it's invisible
        ,axis.title.x=element_text(color="white", size = textsize)
        ,axis.line=element_blank()
        ,axis.text.y=element_blank()
        ,axis.title.y=element_blank()
        ,panel.background=element_blank()
        ,axis.ticks=element_blank()
        # ,plot.margin=unit(c(30,0,0,0), units = "points")
  )

p <- forrest_base +
  geom_linerange(aes(xmin = HR_PFS_CI_lower, xmax = HR_PFS_CI_upper)
  ) + geom_point(aes(x = HR_PFS
                     , size = n_PFS
                     # , fill = IS_dose_70
                     )
                 , shape = 22
                 , fill = "black"
  ) + scale_y_discrete(labels = labels
  ) + labs(x = "hazard ratio (95% CI)"
           ,title = "Progression Free Survival"
  )

if (nrow(data[data$HR_PFS_CI_upper>10,])>0){
  p <- p + 
    geom_segment(data = data[data$HR_PFS_CI_upper>10,]
                 ,aes(x = HR_PFS_CI_lower, xend = Inf, yend = label)
                 ,arrow=arrow(length = unit(.3, "cm"), type = "closed")
    )
}

n <- tab_base + 
  geom_text(aes(label = n_PFS)
  ) + labs(title = "n"
  )

HR <- tab_base +
  geom_text(aes(label = paste0(format(round(HR_PFS,2),nsmall=2,scientific=FALSE)," (",format(round(HR_PFS_CI_lower,2),nsmall=2,scientific=FALSE),"; ", format(round(HR_PFS_CI_upper,2),nsmall=2,scientific=FALSE),")"))
  ) + labs(title = "HR (95% CI)"
  )

dose <- tab_base +
  geom_text(aes(label = IS_dose)
  ) + labs(title = "dose cut-off"
  )

ICI <-dot_base +
  geom_point(aes(color = ICI_homogeneous), size = pointsize, shape = 16
  ) + geom_text(aes(label = ICI_homogeneous), fontface = "bold"
  ) + labs(title = "ICI"
  )

tumour <- dot_base +
  geom_point(aes(color = tumour_homogeneous), size = pointsize, shape = 16
  ) + geom_text(aes(label = tumour_homogeneous), fontface = "bold"
  ) + labs(title = "tumour"
  )

indication <- dot_base +
  geom_point(aes(color = indication_IS_irAE), size = pointsize, shape = 16
  ) + geom_text(aes(label =indication_IS_irAE), fontface = "bold"
  ) + labs(title = "IS only for irAE"
  )

immortal_time_bias <- dot_base +
  geom_point(aes(color = immortal_time_bias), size = pointsize, shape = 16
  ) + geom_text(aes(label =immortal_time_bias), fontface = "bold"
  ) + labs(title = "immortal time"
  )

forrest_GC_PFS <- ggarrange(p,HR,n,dose,ICI,tumour,indication,immortal_time_bias, nrow = 1, widths = c(8,2,1,2,1,1,1,1)
          # ,labels = c("\nProgression Free Survival", "\nHR (95% CI)", "\nn", "dose\ncut-off", "\nICI", "tumour\n", "\nirAE", "indication\n", "\nimmortal time")
          # ,label.x = 0.5, hjust = 0.5, label.y = 1.1
          # ,font.label = list(size =textsize, face = "bold")
) + theme(plot.margin = unit(c(0.5,0.4,0,0), units = "strwidth", data = "immortal time")
          )
forrest_GC_PFS
```

## glucocorticoids - merge and save

Now we merge the OS and PFS plots
```{r echo = T, eval = T, warning = T, error=T, message=T}
data <- data_backup

p_GC_total <- ggarrange(forrest_GC_OS, forrest_GC_PFS, ncol=1
          ,heights = c(nrow(data[!is.na(data$n_OS),])+1.5, nrow(data[!is.na(data$n_PFS),])+1.5)
          )
p_GC_total
```

And we save them with the appropriate dimensions
```{r echo = T, eval = F, warning = T, error=T, message=T}
ggsave("review_IS_ICI_forrestplot_CS.jpg"
       , plot = p_GC_total
       , width = 12.5, height = 9, units = "in"
       , dpi = 1200
       )
```

# 2nd line immunosuppression

Similarly, we can make Figure 3.


```{r echo = T, eval = T, warning = T, error=T, message=T}
data <- `2L_IS`

data <- data.frame(data)
labels <- lapply(1:nrow(data), FUN = function(x) bquote(.(as.character(data[x,"label"])) ^ .(as.character(data[x,"ref"]))))
names(labels) <- data$label

# colnames(data)
dot <- c("control_group", "ICI_homogeneous", "tumour_homogeneous", "irAE_homogeneous", "indication_IS_irAE", 'immortal_time_bias')

for (i in dot){
  data$i<- data.frame(data)[,i]
  data[,i]<- factor(dplyr::recode(data$i,
                                  "low"="+", "Low"="+",
                                  "some concerns"="-", "Some concerns"="-", "Some Concerns"="-", "intermediate"="-", "Intermediate"="-", "adjusted"="-", "Adjusted"="-",
                                  "high"="X", "High"="X",
                                  "unclear"="?", "Unclear"="?", "no information"="?", "No information"="?", "No Information"="?")
                    , levels = c("+", "-", "X", "?"))
  data$i <- NULL
}
```

## 2nd line IS - OS

```{r echo = T, eval = T, warning = T, error=T, message=T}
data_backup <- data
data<- data[!is.na(data$n_OS),]
n_max_subset = max(data$n_OS, na.rm = T)

forrest_base <- ggplot(data, aes(y = label))+
  geom_vline(aes(xintercept=1), linetype = "longdash", color = "darkgrey")+
  scale_size_area(sizelegendtitle, max_size = 6*n_max_subset/n_max_total)+
  scale_x_continuous(trans = "log10")+
  coord_cartesian(xlim = c(.1,10), expand = T)+
  scale_fill_viridis_c(colorlegendtitle, direction = 1)+
  # scale_fill_viridis_d()+
  theme(legend.position = "none"
        # ,legend.key = element_rect(fill = "white")
        ,plot.title = element_text(hjust =0.5, size=textsize, face = "bold")
        ,panel.background = element_blank()
        # ,panel.grid.major = element_line(color = "lightgrey")
        ,axis.line.x = element_line(color = "black")
        ,axis.ticks.y = element_blank()
        ,axis.text.y = element_text(size = textsize, face = "bold", color = "black")
        ,axis.title.y = element_blank()
        ,axis.text.x = element_text(size = textsize, color = "black")
        ,axis.title.x = element_text(size = textsize)
        # ,plot.margin=unit(c(5,0,0,0), units = "lines")
  )

tab_base <- ggplot(data, aes(x=1, y=label)) +
  labs(y=NULL, x= " ") + 
  theme(legend.position="none"
        ,plot.title = element_text(hjust=0.5, size=textsize, face = "bold") ## centering title on text
        ,axis.text.x=element_text(color="white", size = textsize) ## need text to be printed so it stays aligned with figure but white so it's invisible
        ,axis.title.x=element_text(color="white", size = textsize)
        ,axis.line=element_blank()
        ,axis.text.y=element_blank()
        ,axis.title.y=element_blank()
        ,panel.background=element_blank()
        ,axis.ticks=element_blank()
        # ,plot.margin=unit(c(30,0,0,0), units = "points")
  )

dot_base <- ggplot(data, aes(x=1, y=label)) +
  labs(y=NULL, x= " ") + 
  scale_colour_manual(values = c("+"="#02C100", "-"="#E2DF07", "X"="#BF0000", "?"="#4EA1F7"))+
  theme(legend.position="none"
        ,plot.title = element_text(hjust=0.5, size=textsize, face = "bold") ## centering title on text
        ,axis.text.x=element_text(color="white", size = textsize) ## need text to be printed so it stays aligned with figure but white so it's invisible
        ,axis.title.x=element_text(color="white", size = textsize)
        ,axis.line=element_blank()
        ,axis.text.y=element_blank()
        ,axis.title.y=element_blank()
        ,panel.background=element_blank()
        ,axis.ticks=element_blank()
        # ,plot.margin=unit(c(30,0,0,0), units = "points")
  )

p <- forrest_base +
  geom_linerange(aes(xmin = HR_OS_CI_lower, xmax = HR_OS_CI_upper)
  ) + geom_point(aes(x = HR_OS
                     , size = n_OS
                     # , fill = IS_dose_70
  )
  , shape = 22
  , fill = "black"
  ) + scale_y_discrete(labels = labels
  ) + labs(x = "hazard ratio (95% CI)"
           ,title = "Overall Survival"
  )

if(nrow(data[data$HR_OS_CI_upper>10,])>0){
  p<- p + 
    geom_segment(data = data[data$HR_OS_CI_upper>10,]
                 ,aes(x = HR_OS_CI_lower, xend = Inf, yend = label)
                 ,arrow=arrow(length = unit(.3, "cm"), type = "closed")
    )
}

n <- tab_base + 
  geom_text(aes(label = n_OS)
  ) + labs(title = "n"
  )

HR <- tab_base +
  geom_text(aes(label = paste0(format(round(HR_OS,2),nsmall=2,scientific=FALSE)," (",format(round(HR_OS_CI_lower,2),nsmall=2,scientific=FALSE),"; ", format(round(HR_OS_CI_upper,2),nsmall=2,scientific=FALSE),")"))
  ) + labs(title = "HR (95% CI)"
  )

dose <- tab_base +
  geom_text(aes(label = IS_dose)
  ) + labs(title = "comparison"
  )

ICI <-dot_base +
  geom_point(aes(color = ICI_homogeneous), size = pointsize, shape = 16
  ) + geom_text(aes(label = ICI_homogeneous), fontface = "bold"
  ) + labs(title = "ICI"
  )

tumour <- dot_base +
  geom_point(aes(color = tumour_homogeneous), size = pointsize, shape = 16
  ) + geom_text(aes(label = tumour_homogeneous), fontface = "bold"
  ) + labs(title = "tumour"
  )

indication <- dot_base +
  geom_point(aes(color = indication_IS_irAE), size = pointsize, shape = 16
  ) + geom_text(aes(label =indication_IS_irAE), fontface = "bold"
  ) + labs(title = "IS only for irAE"
  )

immortal_time_bias <- dot_base +
  geom_point(aes(color = immortal_time_bias), size = pointsize, shape = 16
  ) + geom_text(aes(label =immortal_time_bias), fontface = "bold"
  ) + labs(title = "immortal time"
  )

forrest_2LIS_OS <- ggarrange(p,HR,n,dose,ICI,tumour,indication,immortal_time_bias, nrow = 1, widths = c(8,2,1,3,1,1,1,1)
                           # ,labels = c("\nOverall Survival", "\nHR (95% CI)", "\nn", "dose\ncut-off", "\nICI", "tumour\n", "\nindication", "immortal time\n")
                           # ,label.x = 0.5, hjust = 0.5, label.y = 1.1
                           ,font.label = list(size =textsize, face = "bold")
                           ,common.legend = T, legend = "none"
) + theme(plot.margin = unit(c(0.5,0.4,0,0), units = "strwidth", data = "immortal time")
)
forrest_2LIS_OS
```

## 2nd line IS - PFS

```{r echo = T, eval = T, warning = T, error=T, message=T}
data <- data_backup
data<- data[!is.na(data$n_PFS),]
n_max_subset = max(data$n_PFS, na.rm = T)


forrest_base <- ggplot(data, aes(y = label))+
  geom_vline(aes(xintercept=1), linetype = "longdash", color = "darkgrey")+
  scale_size_area(sizelegendtitle, max_size = 6*n_max_subset/n_max_total)+
  scale_x_continuous(trans = "log10")+
  coord_cartesian(xlim = c(.1,10), expand = T)+
  scale_fill_viridis_c(colorlegendtitle, direction = 1)+
  # scale_fill_viridis_d()+
  theme(legend.position = "none"
        # ,legend.key = element_rect(fill = "white")
        ,plot.title = element_text(hjust =0.5, size=textsize, face = "bold")
        ,panel.background = element_blank()
        # ,panel.grid.major = element_line(color = "lightgrey")
        ,axis.line.x = element_line(color = "black")
        ,axis.ticks.y = element_blank()
        ,axis.text.y = element_text(size = textsize, face = "bold", color = "black")
        ,axis.title.y = element_blank()
        ,axis.text.x = element_text(size = textsize, color = "black")
        ,axis.title.x = element_text(size = textsize)
        # ,plot.margin=unit(c(5,0,0,0), units = "lines")
  )

tab_base <- ggplot(data, aes(x=1, y=label)) +
  labs(y=NULL, x= " ") + 
  theme(legend.position="none"
        ,plot.title = element_text(hjust=0.5, size=textsize, face = "bold") ## centering title on text
        ,axis.text.x=element_text(color="white", size = textsize) ## need text to be printed so it stays aligned with figure but white so it's invisible
        ,axis.title.x=element_text(color="white", size = textsize)
        ,axis.line=element_blank()
        ,axis.text.y=element_blank()
        ,axis.title.y=element_blank()
        ,panel.background=element_blank()
        ,axis.ticks=element_blank()
        # ,plot.margin=unit(c(30,0,0,0), units = "points")
  )

dot_base <- ggplot(data, aes(x=1, y=label)) +
  labs(y=NULL, x= " ") + 
  scale_colour_manual(values = c("+"="#02C100", "-"="#E2DF07", "X"="#BF0000", "?"="#4EA1F7"))+
  theme(legend.position="none"
        ,plot.title = element_text(hjust=0.5, size=textsize, face = "bold") ## centering title on text
        ,axis.text.x=element_text(color="white", size = textsize) ## need text to be printed so it stays aligned with figure but white so it's invisible
        ,axis.title.x=element_text(color="white", size = textsize)
        ,axis.line=element_blank()
        ,axis.text.y=element_blank()
        ,axis.title.y=element_blank()
        ,panel.background=element_blank()
        ,axis.ticks=element_blank()
        # ,plot.margin=unit(c(30,0,0,0), units = "points")
  )

p <- forrest_base +
  geom_linerange(aes(xmin = HR_PFS_CI_lower, xmax = HR_PFS_CI_upper)
  ) + geom_point(aes(x = HR_PFS
                     , size = n_PFS
                     # , fill = IS_dose_70
  )
  , shape = 22
  , fill = "black"
  ) + scale_y_discrete(labels = labels
  ) + labs(x = "hazard ratio (95% CI)"
           ,title = "Progression Free Survival"
  )

if (nrow(data[data$HR_PFS_CI_upper>10,])>0){
  p <- p + 
    geom_segment(data = data[data$HR_PFS_CI_upper>10,]
                 ,aes(x = HR_PFS_CI_lower, xend = Inf, yend = label)
                 ,arrow=arrow(length = unit(.3, "cm"), type = "closed")
    )
}

n <- tab_base + 
  geom_text(aes(label = n_PFS)
  ) + labs(title = "n"
  )

HR <- tab_base +
  geom_text(aes(label = paste0(format(round(HR_PFS,2),nsmall=2,scientific=FALSE)," (",format(round(HR_PFS_CI_lower,2),nsmall=2,scientific=FALSE),"; ", format(round(HR_PFS_CI_upper,2),nsmall=2,scientific=FALSE),")"))
  ) + labs(title = "HR (95% CI)"
  )

dose <- tab_base +
  geom_text(aes(label = IS_dose)
  ) + labs(title = "comparison"
  )

ICI <-dot_base +
  geom_point(aes(color = ICI_homogeneous), size = pointsize, shape = 16
  ) + geom_text(aes(label = ICI_homogeneous), fontface = "bold"
  ) + labs(title = "ICI"
  )

tumour <- dot_base +
  geom_point(aes(color = tumour_homogeneous), size = pointsize, shape = 16
  ) + geom_text(aes(label = tumour_homogeneous), fontface = "bold"
  ) + labs(title = "tumour"
  )

indication <- dot_base +
  geom_point(aes(color = indication_IS_irAE), size = pointsize, shape = 16
  ) + geom_text(aes(label =indication_IS_irAE), fontface = "bold"
  ) + labs(title = "IS only for irAE"
  )

immortal_time_bias <- dot_base +
  geom_point(aes(color = immortal_time_bias), size = pointsize, shape = 16
  ) + geom_text(aes(label =immortal_time_bias), fontface = "bold"
  ) + labs(title = "immortal time"
  )

forrest_2LIS_PFS <- ggarrange(p,HR,n,dose,ICI,tumour,indication,immortal_time_bias, nrow = 1, widths = c(8,2,1,3,1,1,1,1)
                            # ,labels = c("\nProgression Free Survival", "\nHR (95% CI)", "\nn", "dose\ncut-off", "\nICI", "tumour\n", "\nindication", "immortal time\n")
                            # ,label.x = 0.5, hjust = 0.5, label.y = 1.1
                            # ,font.label = list(size =textsize, face = "bold")
) + theme(plot.margin = unit(c(0.5,0.4,0,0), units = "strwidth", data = "immortal time")
)
forrest_2LIS_PFS
```

## 2nd line IS - merge and save

Merge
```{r echo = T, eval = T, warning = T, error=T, message=T}
data <- data_backup

p_2L_total <- ggarrange(forrest_2LIS_OS, forrest_2LIS_PFS, ncol=1
          ,heights = c(nrow(data[!is.na(data$n_OS),])+1.5, nrow(data[!is.na(data$n_PFS),])+1.5)
          )
p_2L_total
```

Save
```{r echo = T, eval = F, warning = T, error=T, message=T}
ggsave("review_IS_ICI_forrestplot_2L.jpg"
       , plot = p_2L_total
       , width = 12.5, height = 4.8, units = "in"
       , dpi = 1200
       )
```

# R version and packages
```{r echo = T, eval = T, warning = T, error = T, message = T}
sessionInfo()
```
